Data 621---HW1---Regression Model---Version 2

### 2020-09-09 HW1/RegModel_Adler.Rmd
Needed INDEX for casting to work properly!!

# Meltng data from wide to narrow for munging & ggplot; simultaneously removing
# INDEX.
MBmelt <- melt(MB[, -1L], measure.vars = names(MB[, -1L]),
               variable.name = 'Metric', value.name = 'Value',
               variable.factor = FALSE)
```

@@

```{r summaryTable}
# Removing 'TEAM_BATTING_HBP' and index from wide data. Easier to calculate
# correlations later on using wide data.
MB[, `:=`(INDEX = NULL, TEAM_BATTING_HBP = NULL)]

@@

```{r corrgram, fig.height=6}
MBcor <- cor(MB, method = 'pearson', use = 'pairwise.complete.obs')
corrplot(MBcor, 'ellipse', type = 'lower', order = 'hclust',
         col=brewer.pal(n=8, name="RdYlBu"))
```

@@

There are some interesting clusters. For example, `TEAM_FIELDING_E` and 
`TEAM_BATTING_3B` are both negatively correlated with `TEAM_BATTING_SO` and
`TEAM_BATTING_HR`. As regards `TEAM_FIELDING_E`, a hypothesis is that if batters
are either hitting home runs or striking out, *they are***not***getting on base*.
Therefore there are fewer opportunity for fielding errors. Why triples are 
negatively correlated with HRs or SOs is not as logical. There is a positive
correlation between triples and fielding errors of around 51%. Perhaps triples
are more a function of fielding than batting?

@@

@@

```{r reScale}
MBmeltSC <- copy(MBmelt)
MBmeltSC[, Lambda := NULL]
MBmeltUnscale <- MBmeltSC[, .(Mean = mean(Value), SD = sd(Value)),
                          keyby = Metric]

@@

```{r reImputeThenScale}
MBmeltSC <- copy(MBmelt)
MBmeltSC[, Lambda := NULL]
# Remove infinities
MBmeltSC[, Value := ifelse(is.infinite(Value), NA, Value)]
# Center and Scale
MBmeltSC[, Value := replace(Value, is.na(Value), mean(Value, na.rm = TRUE)),
       keyby = Metric]
MBmeltUnscale <- MBmeltSC[, .(Mean = mean(Value), SD = sd(Value)),
                          keyby = Metric]
MBmeltSC[, Value := scale(Value, center = TRUE, scale = TRUE), keyby = Metric]
knitr::kable(MBmeltUnscale, digits = 2L,
             caption = 'Final Post-Transform Data Means and SDs')
ggplot(MBmeltSC, aes(x = Value)) + geom_density() +
  facet_wrap(~ Metric, scales = 'free') +
  ggtitle(label = 'Kernel-Smoothed Densities of Scaled Box-Cox Transformed Data')
```
# Build Models
## Task
Using the training data set, build at least three different multiple linear
regression models, using different variables (or the same variables with
different transformations). Since we have not yet covered automated variable
selection methods, you should select the variables manually (unless you
previously learned Forward or Stepwise selection, etc.). Since you manually
selected a variable for inclusion into the model or exclusion into [*sic*] the
model, indicate why this was done. Discuss the coefficients in the models, do
they make sense? For example, if a team hits a lot of Home Runs, it would be
reasonably expected that such a team would win more games. However, if the
coefficient is negative (suggesting that the team would lose more games), then
that needs to be discussed. Are you keeping the model even though it is counter
intuitive? Why? The boss needs to know.

## Analysis

>>>>

# Meltng data from wide to narrow for munging & ggplot
MBmelt <- melt(MB, id.vars = 'INDEX', variable.name = 'Metric',
               value.name = 'Value', variable.factor = FALSE)
```

@@

```{r summaryTable}
# Removing 'TEAM_BATTING_HBP' and index from wide data. Easier to calculate
# correlations later on using wide data.
MB[, `:=`(TEAM_BATTING_HBP = NULL)]

@@

```{r corrgram, fig.height=6}
MBcor <- cor(MB[, -1L], method = 'pearson', use = 'pairwise.complete.obs')
corrplot(MBcor, 'ellipse', type = 'lower', order = 'hclust',
         col=brewer.pal(n=8, name="RdYlBu"))
```

@@

There are some interesting clusters. For example, `TEAM_FIELDING_E` and 
`TEAM_BATTING_3B` are both negatively correlated with `TEAM_BATTING_SO` and
`TEAM_BATTING_HR`. As regards `TEAM_FIELDING_E`, a hypothesis is that if batters
are either hitting home runs or striking out, *they are* **not**
*getting on base*. Therefore there are fewer opportunity for fielding errors.
Why triples are negatively correlated with home runs or strikeouts is not as
logical. There is a positive correlation between triples and fielding errors of
around 51%. Perhaps triples are more a function of fielding than batting?

@@

# Remove Lambda
MBmelt[, Lambda := NULL]

@@

```{r reScale}
MBmeltSC <- copy(MBmelt)
MBmeltUnscale <- MBmeltSC[, .(Mean = mean(Value), SD = sd(Value)),
                          keyby = Metric]

@@

```{r reImputeThenScale}
MBmeltSC <- copy(MBmelt)
MBmeltSC[, Lambda := NULL]
# Remove infinities
MBmeltSC[, Value := ifelse(is.infinite(Value), NA, Value)]
# Center and Scale
MBmeltSC[, Value := replace(Value, is.na(Value), mean(Value, na.rm = TRUE)),
       keyby = Metric]
MBmeltUnscale <- MBmeltSC[, .(Mean = mean(Value), SD = sd(Value)),
                          keyby = Metric]
MBmeltSC[, Value := scale(Value, center = TRUE, scale = TRUE), keyby = Metric]
knitr::kable(MBmeltUnscale, digits = 2L,
             caption = 'Final Post-Transform Data Means and SDs')
ggplot(MBmeltSC, aes(x = Value)) + geom_density() +
  facet_wrap(~ Metric, scales = 'free') +
  ggtitle(label = 'Kernel-Smoothed Densities of Scaled Box-Cox Transformed Data')
```

# Build Models
## Task
Using the training data set, build at least three different multiple linear
regression models, using different variables (or the same variables with
different transformations). Since we have not yet covered automated variable
selection methods, you should select the variables manually (unless you
previously learned Forward or Stepwise selection, etc.). Since you manually
selected a variable for inclusion into the model or exclusion into [*sic*] the
model, indicate why this was done. Discuss the coefficients in the models, do
they make sense? For example, if a team hits a lot of Home Runs, it would be
reasonably expected that such a team would win more games. However, if the
coefficient is negative (suggesting that the team would lose more games), then
that needs to be discussed. Are you keeping the model even though it is counter
intuitive? Why? The boss needs to know.

## Analysis
At this point we have a set of transformed independent variables on which we
can build a model. The target variable, `TARGET_WINS` does not need to be
scaled. Normally, we would have thrown everything into `caret`, but for the
purposes of this homework, we will use the `stepAIC` function from the `MASS`
package to perform a backwards-stepwise linear regression using AIC as our
goodness of fit metric. For ease, we will cast the dataset we were using from
tall back to wide first.

```{r lm1}
MBsc <- dcast(MBmeltSC, INDEX ~ Metric, value.var = 'Value')
```
